%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape \href{https://www.abdulkhurram.com}{Abdul Rafay Khurram}} \\ \vspace{1pt}
    \small +1 (236) 865-4820 $|$ \href{mailto:rafay@abdulkhurram.com}{\underline{rafay@abdulkhurram.com}} $|$ 
    \href{https://linkedin.com/in/abdulkhurram}{\underline{linkedin.com/in/abdulkhurram}} $|$
    \href{https://github.com/arkb75}{\underline{github.com/arkb75}}
\end{center}

%-----------EDUCATION AND AWARDS-----------
\section{Education \& Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of British Columbia}{Vancouver, BC, Canada}
      {Bachelor of Science in Computer Science (Expected Graduation: May 2027)}{}
      \resumeSubheading
      {Euclid Mathematics Contest, University of Waterloo}{2021}
      {Top 5\% Internationally, Certificate of Distinction}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Software Engineer Intern {\mdseries $|$ \emph{TypeScript/Node.js, AWS, Playwright, OpenAI}}}{Jan. 2025 -- Present}
  {Otto Optical Systems (Contello.ai)}{Toronto, ON, Canada}
  \resumeItemListStart
    \resumeItem{Built cloud-native, event-driven pipelines on \textbf{AWS (SQS/S3)} and multi-brand dashboards with TypeScript/\textbf{Next.js} + \textbf{Node}; owned design→deploy→monitoring (\textbf{CloudWatch}); scaled to \textbf{thousands/day}.}
    \resumeItem{Accelerated content prep by ingesting brand docs with an \textbf{NLP} step and auto-injecting channel-specific context.}
    \resumeItem{Expanded coverage across major platforms with multimedia posting and a \textbf{distributed async video pipeline}; added \textbf{engagement analytics} and Canva export.}
    \resumeItem{Raised scheduler reliability to \textbf{99.9\%} by moving generation to \textbf{OpenAI Responses API}, integrating \textbf{Playwright E2E} gates, hardening auth/session, adding \textbf{retry/backoff} and scheduler-driven notifications.}
  \resumeItemListEnd

    \resumeSubheading
      {Software Developer \& Team Lead {\mdseries $|$ \emph{Unreal Engine, C++, Python}}}{Sept. -- Dec. 2024}
      {UBC Emerging Media Lab}{Vancouver, BC, Canada}
      \resumeItemListStart
        \resumeItem{Led an \textbf{AI-powered} VR platform in \textbf{Unreal Engine (C++)} with interactive UI \textbf{state machines} for clinical scenarios.}
        \resumeItem{Increased stability with a \textbf{multithreaded supervisory layer} that monitors the AI patient and auto-corrects off-protocol replies, using common design patterns.}
      \resumeItem{Delivered a functional prototype in two weeks, securing project funding.}
      \resumeItem{Cut backend costs by \textbf{90\%} via system optimizations, improving real-time performance by \textbf{40\%}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer Intern {\mdseries $|$ \emph{Vue.js, Java, Jenkins, Docker}}}{May -- Aug. 2023}
      {Faaz Consulting}{Maryland, USA}
      \resumeItemListStart
        \resumeItem{Improved UI responsiveness by \textbf{30\%} and redesigned key workflows in Vue.js, delivering a smoother user experience}
        \resumeItem{Automated deployment processes with Jenkins and Docker, reducing deployment times by 20\%.}
        \resumeItem{Enhanced legacy systems and delivered software updates under strict deadlines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{SoloPilot — Client Ops Studio} $|$ \emph{Python, TypeScript/Next.js, AWS, LangChain}}
    {Jun 2025 -- Present}
  \resumeItemListStart
       \resumeItem{Building a human in the loop platform for solo freelancers that unifies client intake, planning, proposals, coding, QA, and delivery in one workspace.}
        \resumeItem{Shipped an email intake console and conversational manager that triages threads, captures scope, and renders versioned proposal PDFs with inline annotations and a revision loop.}
        \resumeItem{Built an evaluator→revisor \textbf{agent} loop with rubric-based \textbf{benchmarking} (score + revision), improving copy quality via measured iterations.}
        \resumeItem{Unified AI and governance: Provider-agnostic \textbf{LLM agent} layer with centralized logging; repo-aware coding/deploy agent; CI quality gates; AWS-backed ops (\textbf{Bedrock}, SQS, versioned S3, CloudWatch).}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{InsightUBC - Dataset Manager} $|$ \emph{React.js, Node.js, REST API}}
    {Sept. -- Dec. 2024}
  \resumeItemListStart
          \resumeItem{Developed React-based dashboards and integrated APIs with Chart.js to visualize live course enrollment data.}
          \resumeItem{Built interactive visualizations with Chart.js, delivering dynamic insights from complex data.}
          \resumeItem{Implemented \textbf{Mocha} and \textbf{Chai} for backend testing, ensuring robust and error-free performance.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Real Estate Management Platform} $|$ \emph{Express.js, OracleDB (SQL)}}
    {July -- August 2023}
  \resumeItemListStart
      \resumeItem{Built a real estate platform integrating inspectors and contractors.}
      \resumeItem{Designed an OracleDB schema with ISA relationships for efficient queries.}
      \resumeItem{Built Express.js APIs with async handling and transactional SQL operations for concurrent listings.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript/JavaScript, Java, Python, SQL, C/C++, Swift, HTML/CSS, React Native} \\
     \textbf{Platforms \& Tools}{: Next.js, Node.js/Express, Playwright; AWS (Amplify, Lambda, DynamoDB, S3, SQS, CloudWatch); OpenAI API; Meta/LinkedIn/X/Canva APIs; Git, Docker, Yarn, Tailwind CSS, RDBMS}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}